Section~\protect\hyperlink{sec:Overview}{1} provides an overview on
SOCRaTEs. Section~\protect\hyperlink{sec:installation}{2} describes how
to install SOCRaTEs and how to create your first SOCRaTEs project.
Section~\protect\hyperlink{sec:using}{3} describes how to use SOCRaTEs.
Finally Section~\protect\hyperlink{sec:tutorial}{4} provides a tutorial
that describes how to use SOCRaTEs on a set of simple examples.

\hypertarget{sec:Overview}{%
\section{Overview}\label{sec:Overview}}

\hypertarget{sec:installation}{%
\section{Installation and Project Creation}\label{sec:installation}}

\hypertarget{prerequisite}{%
\subsection{Prerequisite}\label{prerequisite}}

The following software must be installed on your laptop to run Socrates

\begin{itemize}
\item
  Eclipse (\url{https://www.eclipse.org/})
\item
  Java 1.8 or superior
\item
  Matlab/Simulink
\end{itemize}

\hypertarget{installing-socrates}{%
\subsection{Installing Socrates}\label{installing-socrates}}

Socrates can be installed by performing the following steps:

\begin{itemize}
\item
  Click on Help \(>\) Install new Software \(>\) Add \(>\) Local
\item
  Select the Plugin folder;
\item
  Uncheck Group items by category;
\item
  Select Socrates SDK feature;
\item
  Click on Next \(>\) Next \(>\) I accept \(>\) Finish.
\end{itemize}

\hypertarget{creating-a-new-project}{%
\subsection{Creating a New Project}\label{creating-a-new-project}}

To create a new project perform the following steps:

\begin{itemize}
\item
  File \(>\) New \(>\) Project;
\item
  Select Project from General;
\item
  Click on Finish;
\end{itemize}

\hypertarget{sec:using}{%
\section{Using SOCRaTEs}\label{sec:using}}

\hypertarget{creating-a-your-requirements}{%
\subsection{Creating a your
Requirements}\label{creating-a-your-requirements}}

\begin{itemize}
\item
  Create a file .socrates (File \(>\) New \(>\) File);
\item
  When asked to convert into an Xtext project click on Yes.
\end{itemize}

\hypertarget{generating-the-.m-files-using-socrates}{%
\subsection{Generating the .m files using
Socrates}\label{generating-the-.m-files-using-socrates}}

\begin{itemize}
\item
  copy the file demo.socrates within your workspace.
\item
  Change the file (e.g., add a new blank line) and save it
\item
  When you save the file a file .m is automatically created in the
  folder src-gen/ModelName.
\end{itemize}

\hypertarget{adding-the-oracles-into-your-model}{%
\subsection{Adding the oracles into your
model}\label{adding-the-oracles-into-your-model}}

\begin{itemize}
\item
  Open the Simulink model test
\item
  Copy the file Test\_Req.m into your workspace
\item
  Run Test\_Req in Matlab
\item
  tollerableriskTest\_Req=0;
\item
  Run your simulation
\end{itemize}

\hypertarget{sec:tutorial}{%
\section{Tutorial}\label{sec:tutorial}}
